### 2023-06-16 manuscript.tex
Paul's excellent revisions [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/192b16d94263109406c3457018cf55bec4a36281.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/192b16d94263109406c3457018cf55bec4a36281/checks
https://github.com/stain/2022-fdo-paper/actions/runs/5289312684

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/040dee6cbdcfc6eba52dae0267b6458d68162dba/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/040dee6cbdcfc6eba52dae0267b6458d68162dba}{stain/2022-fdo-paper@040dee6}
on June 16, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/192b16d94263109406c3457018cf55bec4a36281/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/192b16d94263109406c3457018cf55bec4a36281}{stain/2022-fdo-paper@192b16d}
on June 16, 2023.
